### 2022-05-13 main/chapter_2ljets.tex
fix linespacing

\chapter{A search for new phenomena}
\label{chapter:2ljets}

\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert M. Pirsig~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard Feynman~\cite{feynman1974cargo}}
\end{epigraphs}

Our central result is Figure~\ref{fig:2ljets_summary}, which shows the names,
data, and fitted background expectations with error bars in all main regions.
This figure illustrates the background-model part of a \clown{likelihood}
function which is extended with signals to test alternative models.
Exclusion contours testing the addition of C1N2 and GMSB signals to these
backgrounds are shown in Figure~\ref{fig:2ljets_contours}.
Interpretations of discovery region data are displayed in
Table~\ref{tab:2ljets_discovery}.

@@

% upper limits
\begin{table}[tp]
\adjustbox{max width=0.98\textwidth}{%
\centering
\begin{tabular*}{\textwidth}{lccccccc}
{Region} &
\multicolumn{1}{c}{Fitted} &
\multicolumn{1}{l}{Data} &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
\multicolumn{1}{c}{$S_{\mathrm{obs}}^{95}$}  &
\multicolumn{1}{c}{$S_{\mathrm{exp}}^{95}$} &
$\mathrm{CLb}$ &
$p(s=0)~(Z)$  \\[1.5ex]
DR-OffShell      & $22.1\pm2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50~(0.0)$ \\[.5ex]
DR-Low           & $22\pm4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50~(0.0)$ \\[.5ex]
DR-Int           & $35\pm4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23~(0.8)$ \\[.5ex]
DR-High          & $3.9\pm0.5$  & 0  & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50~(0.0)$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51\pm0.20$  & 0  & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50~(0.0)$ \\[.5ex]
\end{tabular*}
}
\caption{%
Upper limit results in discovery region.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right: the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central of $\pm 1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to its observed upper limit,
and the discovery $p$-value capped at $0.5$ with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
}
\label{tab:2ljets_discovery}
\end{table}

>>>>

\begin{singlespacing}
\chapter{A search for new phenomena}
\label{chapter:2ljets}
%
\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert M. Pirsig~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard Feynman~\cite{feynman1974cargo}}
\end{epigraphs}
\end{singlespacing}

Our central result is Figure~\ref{fig:2ljets_summary}, which shows the names,
data, and fitted background expectations with error bars in all main regions.
This figure illustrates the background part of a \clown{likelihood}
which is extended with signals to test alternative models.
Exclusion contours testing the addition of C1N2 and GMSB signals to these
backgrounds are shown in Figure~\ref{fig:2ljets_contours}.
Interpretations of discovery region data are displayed in
Table~\ref{tab:2ljets_discovery}.

\textls[1000]{foo bar}

@@

% upper limits
\begin{table}[tp]
\adjustbox{max width=0.96\textwidth}{%
\centering
\begin{tabular*}{\textwidth}{lccccccc}
{Region} &
\multicolumn{1}{c}{Fitted} &
\multicolumn{1}{l}{Data} &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
\multicolumn{1}{c}{$S_{\mathrm{obs}}^{95}$}  &
\multicolumn{1}{c}{$S_{\mathrm{exp}}^{95}$} &
$\mathrm{CLb}$ &
$p(s=0)~(Z)$  \\[1.5ex]
DR-OffShell      & $22.1\pm2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50~(0.0)$ \\[.5ex]
DR-Low           & $22\pm4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50~(0.0)$ \\[.5ex]
DR-Int           & $35\pm4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23~(0.8)$ \\[.5ex]
DR-High          & $3.9\pm0.5$  & 0  & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50~(0.0)$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51\pm0.20$  & 0  & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50~(0.0)$ \\[.5ex]
\end{tabular*}
}
\caption{%
Upper limit results in discovery region.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right: the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central of $\pm 1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to its observed upper limit,
and the discovery $p$-value capped at $0.5$ with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
{\color{red} TODO add labels and references to asymptotic formulae paper}
}
\label{tab:2ljets_discovery}
\end{table}

### 2022-05-13 main/chapter_experiment.tex
fix linespacing

\chapter{The ATLAS experiment}
\label{chapter:experiment}

\epigraph{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future --- would be interesting if NASA
made a telescope for that%
}%
{Ken M}

>>>>

\begin{singlespacing}
\chapter{The ATLAS experiment}
\label{chapter:experiment}
%
\begin{epigraphs}
\qitem{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future --- would be interesting if NASA
made a telescope for that%
}%
{Ken M}
\end{epigraphs}
\end{singlespacing}

### 2022-05-13 main/chapter_searches.tex
add 2ljets summary plot; replace broken bib file
add exclusion plots
add discovery region results table
fix linespacing

\chapter{Searches in ATLAS}
\label{chapter:intro}

\epigraph{%
One way is to make it so simple that there are \emph{obviously} no deficiencies and the other way is to make it so complicated that there are
no \emph{obvious} deficiencies.%
}%
{Tony Hoare~\cite{hoare2007emperor}}

@@

\section{Frequentist theory}

\epigraph{%
Within this theory, statistical methods of great practical usefulness have been
developed, and its statements can and frequently do contribute in a vague way
to the interpretation of data. \ldots%
}%
{John W. Pratt~\cite{pratt1961testing}}

\section{Post-frequentist practice}

\epigraph{%
\ldots\ But this book, by its very excellence, its thoroughness, lucidity and
precision, intensifies my growing feeling that nevertheless the theory is
arbitrary, be it however ``objective,'' and the problems it solves, however
precisely it may solve them, are not even simplified theoretical counterparts
of the real problems to which it is applied.%
}%
{John W. Pratt~\cite{pratt1961testing}}

>>>>

\begin{singlespacing}
\chapter{Searches in ATLAS}
\label{chapter:intro}
%
\begin{epigraphs}
\qitem{%
One way is to make it so simple that there are \emph{obviously} no deficiencies
and the other way is to make it so complicated that there are no \emph{obvious}
deficiencies.%
}%
{Tony Hoare~\cite{hoare2007emperor}}
\end{epigraphs}
\end{singlespacing}

@@

\section{Frequentist theory}
\begin{epigraphs}
\qitem{%
Within this theory, statistical methods of great practical usefulness have been
developed, and its statements can and frequently do contribute in a vague way
to the interpretation of data. \ldots%
}%
{John W. Pratt~\cite{pratt1961testing}}
\end{epigraphs}

\section{Post-frequentist practice}
\begin{epigraphs}
\qitem{%
\ldots\ But this book, by its very excellence, its thoroughness, lucidity and
precision, intensifies my growing feeling that nevertheless the theory is
arbitrary, be it however ``objective,'' and the problems it solves, however
precisely it may solve them, are not even simplified theoretical counterparts
of the real problems to which it is applied.%
}%
{John W. Pratt~\cite{pratt1961testing}}
\end{epigraphs}

% significancen measures
The ATLAS-recommended~\cite{atlas_significance} significance measure is
\begin{equation}
\label{eqn:significance_atlas}
S_\mathrm{ATLAS}(n, \mu, \sigma)
= \mathrm{sgn}(n - \mu) \sqrt{2\left(
    n\log\left(\frac{n(\mu + \sigma^2)}{\mu^2 + n\sigma^2}\right)
    - \frac{\mu^2}{\sigma^2}\log\left(
        1 + \frac{\sigma^2(n - \mu)}{\mu(\mu + \sigma^2)}
    \right)
\right)}
~.
\end{equation}
